### 2024-03-21 paper.tex
removed \scriptsize
added Ana's e-mail address

In the present paper, we discuss strategies to analyze single-cell bisulfite-sequencing (scBS) data.
We suggest improvements to current approaches, and demonstrate their value in benchmarks, using \new{four} real-world datasets.
Furthermore, we discuss how to perform comparative analyses.
Finally, we present \textit{MethSCAn}, a comprehensive software toolkit to perform scBS data analysis, using the described methods.
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}

@@

As an alternative, we suggest to consider the residuals of the individual CpG methylation values $x_{ij}$ from the smoothed average $\tilde x_i$,
\[ r_{ij} = x_{ij} - \tilde x_i, \]
and averaging over these, obtaining
\begin{equation} 
r_{Ij} = \frac{\scriptsize{1}}{\scriptsize{|I\cap C_i|+1}}\sum_{i\in I\cap C_i}\left( x_{ij} - \tilde x_i \right).
\label{avgres}
\end{equation}

@@

\begin{equation} 
v_I = \frac{\scriptsize{1}}{\scriptsize{|C_I|}}\sum_{j\in C_I}\left( r_{Ij} - \langle r_{Ij'}\rangle_{j'\in C_I} \right)^2, \label{var}
\end{equation}

>>>>

In the present paper, we discuss strategies to analyze single-cell bisulfite-sequencing (scBS) data.
We suggest improvements to current approaches, and demonstrate their value in benchmarks, using \new{four} real-world datasets.
Furthermore, we discuss how to perform comparative analyses.
Finally, we present \textit{MethSCAn}, a comprehensive software toolkit to perform scBS data analysis, using the described methods.
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mails:  \texttt{l.kremer@dkfz-heidelberg.de}, \hspace{1cm}\texttt{a.martin-villalba@dkfz-heidelberg.de}, \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}

@@

As an alternative, we suggest to consider the residuals of the individual CpG methylation values $x_{ij}$ from the smoothed average $\tilde x_i$,
\[ r_{ij} = x_{ij} - \tilde x_i, \]
and averaging over these, obtaining
\begin{equation} 
r_{Ij} = \frac{1}{|I\cap C_i|+1}\sum_{i\in I\cap C_i}\left( x_{ij} - \tilde x_i \right).
\label{avgres}
\end{equation}

@@

\begin{equation} 
v_I = \frac{1}{|C_I|}\sum_{j\in C_I}\left( r_{Ij} - \langle r_{Ij'}\rangle_{j'\in C_I} \right)^2, \label{var}
\end{equation}
